Can Zero-shot LLMs save additional work in machine learning prioritised screening for systematic reviews?

### 2024-11-04 LLMs/manuscript/main.tex

	There is a large literature \cite{omara-eves_using_2015}, going back nearly 20 years \cite{cohen_reducing_2006}, that investigates how machine learning might be used to automate parts of this process, in order to reduce the labour required to complete a systematic review. However, much of this literature demonstrates how one approach or another \textit{would have been able to} save work on past reviews where complete evaluation datasets are available, without showing how the approach could be used to \textit{responsibly} save work in new reviews where the inclusion and exclusion decisions are not known \textit{a priori}.

@@

	Early attempts to automate systematic review screening used simple models like logistic regression and support vector machines. Lately, the literature on automating systematic reviews has increasingly turned its attention to the use of large language models (LLMs). However, not enough attention has been paid to comparing LLM-based approaches with the much simpler (and computationally less expensive) alternatives. Further, papers which have investigated the use of LLMs have so far not considered how they might be used in a responsible manner where evaluation data is not available.

@@

    Similarly, a paper by Xia and co-authors \cite{xia_llmscreen_2024} highlights the lack of commonly agreed upon stopping criteria as a limitation of current approaches to ml-assisted screening, and proposes LLM-based screening as a solution.

>>>>

	There is a large literature \cite{omara-eves_using_2015}, going back nearly 20 years \cite{cohen_reducing_2006}, that investigates how machine learning might be used to automate parts of this process, in order to reduce the labour required to complete a systematic review. However, much of this literature introduces new tools, or demonstrates how one approach or another \textit{would have been able to} save work on past reviews where complete evaluation datasets are available, without showing how the approach could be used to \textit{responsibly} save work in new reviews where the inclusion and exclusion decisions are not known \textit{a priori}  \cite{van_de_schoot_open_2021, rathbone_faster_2015, yang_goldilocks_2022}.

@@

	Early attempts to automate systematic review screening used simple models like logistic regression and support vector machines \cite{cohen_reducing_2006}. Lately, the literature on automating systematic reviews has increasingly turned its attention to the use of large language models (LLMs) \cite{oami_performance_2024, wang_zero-shot_2024, luo_evaluating_2024, xia_llmscreen_2024}. However, not enough attention has been paid to comparing LLM-based approaches with the much simpler (and computationally less expensive) alternatives. Further, papers which have investigated the use of LLMs have so far not considered how they might be used in a responsible manner where evaluation data is not available.

@@

    Similarly, a paper by Xia and co-authors \cite{xia_llmscreen_2024} highlights the lack of commonly agreed upon stopping criteria as a limitation of current approaches to ml-assisted screening, and proposes LLM-based screening as a solution. However, replacing one type of model with another does not solve the problem of how to quantify the risk of model error negatively affecting the study through missed reviews. Large language models do not possess properties that mean that we do not need to think carefully about how they are evaluated and used responsibly.
